On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-22 paper/paper.tex
Table showing the relationship between things from the Church encoding section and the things from the rest of the paper

\subsection{Connection to Church encodings}
\begin{todo}
  Work on this subsection
\end{todo}

@@

@@

  Does our way of handling recursive types correspond to how any of
  those encodings handle recursive types?
\end{todo}

>>>>

\subsection{Connection to Church encodings}
\begin{todo}
  Work on this subsection. Maybe this shouldn't be a separate section at all and
  maybe its contents should be incorporated throughout the rest of the paper.
\end{todo}

@@

Comparing this back to our larger encoding, there is the correspondence: \\

\begin{tabular}{|l|l|}
  \hline
  \ttt{ChurchCoproductMatch} & \ttt{SumMatchExp} \\
  \ttt{ChurchProductMach} & \ttt{ProdMatchExp} \\
  \ttt{CoproductMatch} & \ttt{SumMatch} \\
  \ttt{ProductMatch} & \ttt{ProdMatch} \\
  \ttt{ChurchLam} & \ttt{Lam} \\
  \hline
\end{tabular} \\

@@

  Does our way of handling recursive types correspond to how any of
  those encodings handle recursive types?

  Maybe this is relevant: \href{https://www.reddit.com/r/haskell/comments/hvlh6a/generalized_church_encoding_is_the_curryhoward_of/}{\color{blue}{Generalized Church encoding is the Curry-Howard of Knaster-Tarski}}
\end{todo}
